Extracting The Power of Dependent Types

### 2021-09-24 paper.tex
Add my orcid + acknowledge NWO

%% Author with single affiliation.
\author[J. Cockx]{Jesper Cockx}
%\authornote{with author1 note}          %% \authornote is optional;
                                         %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{%
  \institution{TU Delft}
  \city{Delft}
  \postcode{2628 XE}
  \country{Netherlands}}
\email{j.g.h.cockx@tudelft.nl}           %% \email is recommended

@@

\begin{acks}
We would like to thank reviewers for their constructive suggestions.
This work is supported by the \grantsponsor{EPSRC}{Engineering and Physical
Sciences Research Council}{https://epsrc.ukri.org} through the grant
\grantnum{EPSRC001}{EP/N028201/1}.
\end{acks}

>>>>

%% Author with single affiliation.
\author[J. Cockx]{Jesper Cockx}
%\authornote{with author1 note}          %% \authornote is optional;
                                         %% can be repeated if necessary
\orcid{0000-0003-3862-4073}              %% \orcid is optional
\affiliation{%
  \institution{TU Delft}
  \city{Delft}
  \postcode{2628 XE}
  \country{Netherlands}}
\email{j.g.h.cockx@tudelft.nl}           %% \email is recommended

@@

\begin{acks}
We would like to thank reviewers for their constructive suggestions.
This work is supported by the \grantsponsor{EPSRC}{Engineering and
Physical Sciences Research Council}{https://epsrc.ukri.org} through
the grant \grantnum{EPSRC001}{EP/N028201/1}, and the
\grantsponsor{NWO}{Dutch Research Council}{https://www.nwo.nl/en}
through the grant VI.Veni.202.216.
\end{acks}
